Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2021-09-06 vertical-thermal-review.Rmd
added the note we had for Table 2
ie. **composite climatic stress variable from canopy temperature, vapour pressure deficit, and relative humidity
is higher in lower canopy

** (**NIDHI, we previously had a footnote here. I believe it's the savanna site. I can't find that, though.**)
```{r eval=FALSE, echo=FALSE}
# refs in this table currently in the nocite field at top of document 
```

>>>>

** composite climatic stress variable from canopy temperature, vapour pressure deficit, and relative humidity is higher in lower canopy
```{r eval=FALSE, echo=FALSE}
# refs in this table currently in the nocite field at top of document 
```
